---
title: "Estimating DCMs - Solutions"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
library(measr)
library(fs)

if (!dir_exists("fits")) dir_create("fits")
```

## Exercise 1

View the MacReady & Dayton (1977) data (`mdm_data` and `mdm_qmatrix`).

1. How many items are in the data?
2. How many respondents are in the data?
3. How many attributes are measured?

```{r}
# 142 rows = 142 respondents
# 4 non-ID columns = 4 items
mdm_data

# 4 rows = 4 items
# 1 non-ID column = 1 attribute (multiplication)
mdm_qmatrix
```

## Exercise 2

Complete the `parameters` and `transformed parameters` blocks for the MDM data.

```{stan output.var="mdm_lcdm", eval = FALSE}
data {
  int<lower=1> I;           // # of items
  int<lower=1> R;           // # of respondents 
  int<lower=1> A;           // # of attributes
  int<lower=1> C;           // # of attribute profiles (latent classes) 
  matrix[R,I] y;            // response matrix
}
parameters {
  simplex[C] Vc;
  
  // item parameters
  real l1_0;
  real<lower=0> l1_11;
  real l2_0;
  real<lower=0> l2_11;
  real l3_0;
  real<lower=0> l3_11;
  real l4_0;
  real<lower=0> l4_11;
}
transformed parameters {
  matrix[I,C] PImat;
  
  PImat[1,1] = inv_logit(l1_0);
  PImat[1,2] = inv_logit(l1_0 + l1_11);
  PImat[2,1] = inv_logit(l2_0);
  PImat[2,2] = inv_logit(l2_0 + l2_11);
  PImat[3,1] = inv_logit(l3_0);
  PImat[3,2] = inv_logit(l3_0 + l3_11);
  PImat[4,1] = inv_logit(l4_0);
  PImat[4,2] = inv_logit(l4_0 + l4_11);
}
model {
  for (r in 1:R) {
    real ps[C];
    for (c in 1:C) {
      real log_items[I];
      for (i in 1:I) {
        log_items[i] = y[r,i] * log(PImat[i,c]) + (1 - y[r,i]) * log(1 - pi[i,c]);
      }
      ps[c] = log(Vc[c]) + sum(log_items);
    }
    target += log_sum_exp(ps);
  }
}
```

## Exercise 3

Estimate and LCDM on the MDM data. Your model should have:

* 2 chains
* 1000 warmup and 500 sampling iterations
* Use whichever backend you prefer

```{r}
mdm_lcdm <- measr_dcm(
  data = mdm_data, qmatrix = mdm_qmatrix,
  resp_id = "respondent", item_id = "item",
  type = "lcdm",
  method = "mcmc", backend = "cmdstanr",
  iter_warmup = 1000, iter_sampling = 500, chains = 2,
  file = "fits/mdm-lcdm"
)
```

## Exercise 4

What proportion of respondents have mastered multiplication in the MDM data?

What is the probability that respondent zfn2i has mastered multiplication?

```{r}
measr_extract(mdm_lcdm, "strc_param")

mdm_lcdm <- add_respondent_estimates(mdm_lcdm)
measr_extract(mdm_lcdm, "attribute_prob")
```

## Exercise 5

Estimate a new LCDM model for the MDM data with the following priors:

* Intercepts: `normal(-1, 2)`
  * Except item 3, which should use a `normal(0, 1)` prior
* Main effects: `lognormal(0, 1)`

Extract the prior to see that the specifications were applied

```{r}
new_mdm <- measr_dcm(
  data = mdm_data, qmatrix = mdm_qmatrix,
  resp_id = "respondent", item_id = "item",
  type = "lcdm",
  prior = c(prior(normal(-1, 2), class = "intercept"),
            prior(normal(0, 1), class = "intercept", coef = "l3_0")),
  method = "mcmc", backend = "cmdstanr",
  iter_warmup = 1000, iter_sampling = 500, chains = 2,
  file = "fits/mdm-new-prior"
)

measr_extract(new_mdm, "prior")
```
